\begin{english} %switch to English language rules

\chapter[Abstract]{Abstract\protect\footnote{The following content is translated from the German version with the help of DeepL (\url{https://www.deepl.com/de/translator})}}

Rapid technological change requires companies such as RZL Software GmbH to continuously adapt, presenting them with strategic and technical challenges. Converting older software systems usually involves an enormous amount of resources. In terms of efficiency, a targeted selection of functionalities based on user data can lead to significant improvements. Furthermore, established processes can be identified, maintained and optimised for users of the existing software product.

While standard solutions for determining user data already exist in the web environment, this is not the case for complex Windows Forms and WPF rich client applications. This bachelor's thesis therefore deals with the development of an activity tracking framework that can be used flexibly for WPF and Windows Forms applications. This framework should make it possible to send behavioural data to the company without making any major changes to the existing system and without impairing the use of the programme.

The thesis begins with a comparison of different technologies and the development of the basics. Based on this, the concept for the framework is created. The system is then implemented using C\# and integrated into a WPF and a Windows Forms application for testing purposes. To demonstrate its functionality, a configuration is created and relevant data is determined from the existing system. This data also forms the basis for answering questions that have arisen as a result of the optimisation problem.

\end{english}

